---
title: "Untitled"
author: "Boyi Guo"
institute: |
  | Department of Biostatistics
  | University of Alabama at Birmingham
date: "August 8th, 2021 "
output: 
  beamer_presentation:
    keep_tex: FALSE
    theme: "Szeged"
    colortheme: "spruce"
    toc: FALSE
    number_section: FALSE
    slide_level: 3
    includes:
      in_header: "preamble.tex"
classoption: "aspectratio=169"
bibliography:
  - bibfile.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Outline
  - Self-introduction
  - Multivariate Outcome Treatment Effect Random Forest (MOTE RF)
  - Bayesian Hierarchical Additive Model
  - Epidemiology Study
  - Future Directions

# MOTE RF
### Motivation
- A study about different forms of almond diet (whole almond Vs processed almond) on improving biomarkers
  - Balanced two-arm randomized trial
  - Microbiomes and Biomarkers are measured pre- and post- intervention
  
- How would the treatment effect of improving the biomarker be different regarding their pre-treatment microbiome status
  - treatment effect

### Challenges
- Unobservable treatment effect
- Multivariate outcome
- Pre- and Post- collected data
- Correlation structure among predictors and outcomes

### Assumptions

# BHAM {.unlisted}
```{r child = "02-BHAM.Rmd"}
```

# Collaborative Projects


# Future Direction

# Closing Remarks

### BHAM Simulation Study {.unlisted .unnumbered}
* Follow the data generating process introduced in @Bai2020. 
* $n_{train} = 500$, $n_{test}=1000$
* $p=4, 10, 50, 200$
$$
\mu = 5 \sin(2\pi x_1) - 4 \cos(2\pi x_2 -0.5) + 6(x_3-0.5) - 5(x_4^2 -0.3),
$$

* $f_j(x_j) = 0$ for $j = 5, \dots, p$.
* 2 types of outcome: Gaussian ($\phi=1$), Binomial
* Splines are constructed using 10 knots
* 50 Iterations

### Comparison & Metircs {.unlisted .unnumbered}
* Methods of comparison
  * Proposed model with EM-CD and EM-IWLS
  * mgcv [@Wood2004]
  * COSSO [@Zhang2006GAM] and adaptive COSSO[@Storlie2011]
  * Sparse Bayesian GAM [@Bai2021]

* Metrics
  * out-of-sample $R^2$ for continuous outcomes
  * out-of-sample AUC for binary outcomes
  
### Out-of-sample AUC {.unlisted .unnumbered}

* The proposed method works better in low, medium, high settings than other state-of-art methods
* SB-GAM works better in ultra-high setting

\begin{tabular}{r|l|l|l|l|l|l}
\hline
p & EM-IWLS & EM-CD & COSSO & ACOSSO & mgcv & SB-GAM\\
\hline
4 & \textbf{0.94 (0.01)} & 0.89 (0.04) & 0.90 (0.02) & 0.90 (0.02) & 0.94 (0.01) & 0.93 (0.01)\\
\hline
10 & \textbf{0.93 (0.01)} & 0.87 (0.03) & 0.87 (0.03) & 0.85 (0.03) & 0.92 (0.04) & 0.92 (0.01)\\
\hline
50 & \textbf{0.92 (0.01)} & 0.87 (0.02) & 0.83 (0.02) & 0.83 (0.02) & 0.76 (0.04) & 0.92 (0.01)\\
\hline
200 & 0.88 (0.01) & 0.86 (0.02) & 0.81 (0.06) & 0.81 (0.08) & - & \textbf{0.92 (0.01)}\\
\hline
\end{tabular}  

# References {.allowframebreaks}
